Large and Infinitary Quotient Inductive-Inductive Types

### 2020-06-23 draft/paper.tex
add hyperref
nicer refs

\usepackage[utf8]{inputenc}
\usepackage{amsmath}
\usepackage{amsthm}
\usepackage{amssymb}
\usepackage{amsfonts}
\usepackage{mathpartir}
\usepackage{scalerel}
\usepackage{stmaryrd}
\usepackage{authblk}

\bibliographystyle{acm}

@@

\textbf{Acknowledgments.} The first author was supported by the European Union,
co-financed by the European Social Fund (EFOP-3.6.3-VEKOP-16-2017-00002). The
second author was supported by the National Research, Development and Innovation
Fund of Hungary, financed under the Thematic Excellence Programme funding
scheme, Project no. ED18-1-2019-0030 (Application-specific highly reliable IT
solutions), by the New National Excellence Program of the Ministry for
Innovation and Technology, Project no. \'UNKP-19-4-ELTE-874, and by the Bolyai
Fellowship of the Hungarian Academy of Sciences, Project no. BO/00659/19/3.

>>>>

\usepackage[utf8]{inputenc}
\usepackage[hidelinks]{hyperref}
\usepackage{amsmath}
\usepackage{amsthm}
\usepackage{amssymb}
\usepackage{amsfonts}
\usepackage{mathpartir}
\usepackage{scalerel}
\usepackage{stmaryrd}
\usepackage{authblk}

\bibliographystyle{IEEEtran}

@@

\paragraph{Acknowledgments.}The first author was supported by the European Union,
co-financed by the European Social Fund (EFOP-3.6.3-VEKOP-16-2017-00002). The
second author was supported by the National Research, Development and Innovation
Fund of Hungary, financed under the Thematic Excellence Programme funding
scheme, Project no. ED18-1-2019-0030 (Application-specific highly reliable IT
solutions), by the New National Excellence Program of the Ministry for
Innovation and Technology, Project no. \'UNKP-19-4-ELTE-874, and by the Bolyai
Fellowship of the Hungarian Academy of Sciences, Project no. BO/00659/19/3.
